%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% This is a modified ONE COLUMN version of
% the following template:
% 
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{Kevin}{Mankowski}{ \urlstyle{same}
\href{mailto:kevin.mankowski@gatech.edu}{kevin.mankowski@gatech.edu}\space\space|\space\space(703) 939-1134\space\space|\space\space\href{https://github.com/KMankowski}{github.com/KMankowski}
}

% \href{kevinmankowski.me}{kevinmankowski.me}

\section{Education}
\runsubsection{Georgia Institute of Technology}
\descript{| BS Computer Science}
\location{Aug 2020 - May 2023 | Atlanta, GA}
\sectionsep

\runsubsection{George Mason University}
\descript{| BS Computer Science}
\location{Aug 2019 - May 2020 | Fairfax, VA}
Cum. GPA: 3.9 / 4.0 \textbullet{}
Major GPA: 4.0 / 4.0
\sectionsep

\section{Skills}
\begin{minipage}[t]{.4\textwidth}
\subsection{Software}
\location{Languages:}
Java \textbullet{} Python \textbullet{} C \textbullet{} HTML/CSS\ \\
\location{Frameworks:}
Bootstrap \textbullet{} JavaFX\ \\
\location{Technologies:}
Git \textbullet{} Docker \textbullet{} Kubernetes
\sectionsep
\end{minipage}
\hfill
\begin{minipage}[t]{.5\textwidth}
\subsection{Coursework}
\location{Fall 2020:}
Objects and Design \textbullet{} Computer Organization\ \\
\location{Spring 2020:}
{\fontspec[Path = fonts/lato/]{Lato-Bol}\fontsize{9.5pt}{9.5pt}\selectfont\raggedright\bfseries{Data Structures}} \textbullet{} Linear Algebra\ \\
\location{Fall 2019:}
Object-Oriented Programming \textbullet{} Essentials of CS
\end{minipage}
\sectionsep

\section{Experience}

\runsubsection{Software Engineer Intern}
\descript{| Lockheed Martin Corporation}
\location{Jun 2020 – Aug 2020 | Manassas, VA \textbullet{} Secret Clearance}

\begin{tightemize}
\item Supported team in the transitioning of applications to a cloud-based microservices architecture.
\item Researched capabilities and functionalities of Docker, Kubernetes, and cloud storage solutions such as Ceph.
\item Configured testbeds via Red Hat Enterprise Linux for their implementation and use, documenting concepts and procedures for unit-wide distribution.
\item Presented weekly internship progress reports to my team of software engineers.
\end{tightemize}
\sectionsep

\runsubsection{Teaching Assistant}
\descript{| George Mason University}
\location{Jan 2020 – May 2020 | Fairfax, VA}
\begin{tightemize}
\item Taught and supported students in their first course on {\fontspec[Path = fonts/lato/]{Lato-Bol}\fontsize{9.5pt}{9.5pt}\selectfont\raggedright\bfseries{Object-Oriented Programming}} with {\fontspec[Path = fonts/lato/]{Lato-Bol}\fontsize{9.5pt}{9.5pt}\selectfont\raggedright\bfseries{Java}}.
\item Resolved questions via online discussion board, aided students during weekly labs, and reviewed all upcoming projects and lab assignments.
\end{tightemize}
\sectionsep

\runsubsection{Programming Tutor}
\descript{| Code Ninjas}
\location{Apr 2019 – Jul 2020 | Gainesville, VA}
\begin{tightemize}
\item Mentored children ages 7-14 on foundational programming skills using {\fontspec[Path = fonts/lato/]{Lato-Bol}\fontsize{9.5pt}{9.5pt}\selectfont\raggedright\bfseries{Scratch}} and {\fontspec[Path = fonts/lato/]{Lato-Bol}\fontsize{9.5pt}{9.5pt}\selectfont\raggedright\bfseries{JavaScript}}.
\end{tightemize}
\sectionsep

\section{Projects}
\runsubsection{Parking Reservation System}
\descript{| Java, JavaFX, Google Maps API}
\begin{tightemize}
\item Created a mock application to allow members of the university to efficiently reserve spots at various times. 
\item Incorporated the Google Maps API to determine the closest parking lot to a user's destination.
\end{tightemize}
\sectionsep

\runsubsection{Osu! Account Web Scraper}
\descript{| Python, Selenium}
\begin{tightemize}
\item Implemented web scrapers to compile pertinent information of a provided rhythm game account. 
\item Currently developing a Django application utilizing that functionality to track community contributions of users.
\end{tightemize}
\sectionsep

\runsubsection{GMU Student-Run Computing}
\descript{| HTML/CSS}
\begin{tightemize}
\item Contributed to software tailored to assist both students and faculty of the University community.
\item Designed and implemented a dark mode for our largest web application, provided incremental updates to the organization website, and created materials to help orient new members.
\end{tightemize}

\end{document}  \documentclass[]{article}